ranacapa: An R package to explore environmental DNA data with exploratory statistics and interactive visualizations

### 2018-10-08 manuscript.Rmd
edits from RSM

## Author contributions
GSK led the development of ranacapa, with help from MCC. ZJG and EEC provided feedback regarding which analyses and visualization options to include. ZJG performed the MPA eDNA study in collaboration with JS and DK. NK, GSK, EC, and RM collaborated with AF and JMP, who used `ranacapa` in their microbiology undergraduate course. GSK wrote the first draft of this manuscript; all authors contributed to revisions.

@@

## Grant information
GSK and ZJG were supported by the US-NSF Graduate Research Fellowship (DEG No. 1650604). EEC is supported by the CALeDNA program, with funds from University of California President’s Research Catalyst Award (CA-16-376437).

>>>>

## Author contributions
GSK led the development of ranacapa, with help from MCC. ZJG and EEC provided feedback regarding which analyses and visualization options to include. ZJG performed the MPA eDNA study in collaboration with JS and DK. NJBK, GSK, EEC, and RSM collaborated with AF and JMP, who used `ranacapa` in their microbiology undergraduate course. GSK wrote the first draft of this manuscript; all authors contributed to revisions.

@@

## Grant information
GSK and ZJG were supported by the US-NSF Graduate Research Fellowship (DEG No. 1650604). EEC, RSM, and the CALeDNA program are supported by the University of California President’s Research Catalyst Award (CA-16-376437).
